Minicaml, a purely functional, didactical programming language with an interactive REPL.

### 2019-12-25 paper/paper.tex
added more primitives, added bisect_ppx for test coverage, added more test cases

\begin{abstract}
\textbf{minicaml} is a small, purely functional interpreted programming language
with a didactical purpose. It is based on the Prof. Gianluigi Ferrari and Prof.
Francesca Levi's minicaml, an evaluation example to show students attending the
Programming 2 course at the University of Pisa how interpreters work. It is an
interpreted language with a Caml-like syntax, featuring interchangeable eager
and lazy evaluation and a didactical REPL that shows each AST expression and
each evaluation step.
\end{abstract}
\end{titlingpage}

>>>>

\begin{abstract}
\textbf{minicaml} is a small, purely functional interpreted programming language
with a didactical purpose. It is based on the Prof. Gianluigi Ferrari and Prof.
Francesca Levi's minicaml, an evaluation example to show students attending the
Programming 2 course at the University of Pisa how interpreters work. It is an
interpreted language featuring a Caml-like syntax, static (lexical scoping),
interchangeable eager and lazy evaluation and a didactical REPL that
shows each AST expression and each evaluation step.
\end{abstract}
\end{titlingpage}
